Driver coverage

### 2024-02-07 scomatic/reports/driver_coverage.Rmd
fix infercnv metadata propagation, change to standard mappings and annotations, add help nf functions
update driver coverage functions

#knitr::opts_knit$set(root.dir = '../')
knitr::opts_chunk$set(
  warning = FALSE, 
  dpi = 300, 
  message = FALSE,
  cache.path = params$cache_dir)

@@

  # get all positions in each gene
  gene_spans <-
    ref_cds[c(drivers$gene)] %>%
    purrr::map(function(i) {
      tibble::tibble(
        chr = as.character(i$chr),
        start = i$intervals_cds[, 1],
        end = i$intervals_cds[, 2]) %>%
        dplyr::mutate(exon = paste0('exon', dplyr::row_number()))
    })

  # drop those not found
  gene_spans[is.na(names(gene_spans))] <- NULL

@@

```{r knit_plots, echo = F, warning = F, message = F, results = 'asis'}
chunks <- c()

@@

```{r mean_coverage}
cov %>%
  dplyr::filter(lvl == 'drivers_samtools_depth') %>%
  dplyr::group_by(sample, gene, feature) %>%
  dplyr::summarise(mean_depth = mean(depth)) %>%
  ggplot(aes(x = sample, y = mean_depth, fill = feature)) +
  geom_col(position = 'dodge') +
  facet_grid(gene ~ .) +
  theme_classic()
```

>>>>

knitr::opts_chunk$set(
  warning = FALSE, 
  dpi = 300, 
  message = FALSE,
  cache.path = params$cache_dir)

@@

  # only drivers in ref_cds
  avail_drivers <-
    drivers %>%
    dplyr::filter(gene %in% names(ref_cds))

  # get all positions in each gene
  gene_spans <-
    ref_cds[c(avail_drivers$gene)] %>%
    purrr::map(function(i) {
      tibble::tibble(
        chr = as.character(i$chr),
        start = i$intervals_cds[, 1],
        end = i$intervals_cds[, 2]) %>%
        dplyr::mutate(exon = paste0('exon', dplyr::row_number()))
    })

@@

```{r knit_plots, echo = F, message = F, results = 'asis', warning = T, error = T}
chunks <- c()

@@

```{r mean_coverage, eval = F}
cov %>%
  dplyr::filter(lvl == 'drivers_samtools_depth') %>%
  dplyr::group_by(sample, gene, feature) %>%
  dplyr::summarise(mean_depth = mean(depth)) %>%
  ggplot(aes(x = sample, y = mean_depth, fill = feature)) +
  geom_col(position = 'dodge') +
  facet_grid(gene ~ .) +
  theme_classic()
```
